### 2016-01-18 paper.tex
No need to repeat 'tip speed ratio'

Reference Model 2 (RM2) is a dual-rotor, vertical-axis cross-flow river turbine
that was designed to operate in a reach of the lower Mississippi River near
Baton Rouge, Louisiana \cite{Barone2011, Neary2011}. The rotor has three blades,
a relatively low solidity $Nc/(\pi D)$ or chord-to-radius ratio $c/R$, and a
preliminary analysis with Sandia's CACTUS vortex line numerical model
\cite{Murray2011} predicted a full-scale performance coefficient of 47\% at 1
m/s flow speed and a tip speed ratio $\lambda \equiv \frac{\omega R}{U_\infty} =
3.15$ \cite{Barone2011}, where $\omega$ and $R$ are the rotor's angular velocity
and radius, respectively. An initial experimental measurement campaign with a
1:15 scale RM2 rotor conducted at the Saint Anthony Falls Laboratory (SAFL) at
the University of Minnesota resulted in maximum power coefficient of
approximately 5\% at a tip speed ratio $\lambda = 2.2$. This discrepancy between
numerical and physical model performance prompted the experimental measurements
presented here, namely due to the low Reynolds number---$Re_D = U_\infty D /
\nu$, where $U_\infty$ is the free stream velocity, $D$ is the rotor diameter,
and $\nu$ is the fluid kinematic viscosity---of the 1:15 scale tests, which were
performed at $Re_D \sim 10^5$ \cite{Hill2014}.

>>>>

Reference Model 2 (RM2) is a dual-rotor, vertical-axis cross-flow river turbine
that was designed to operate in a reach of the lower Mississippi River near
Baton Rouge, Louisiana \cite{Barone2011, Neary2011}. The rotor has three blades,
a relatively low solidity $Nc/(\pi D)$ or chord-to-radius ratio $c/R$, and a
preliminary analysis with Sandia's CACTUS vortex line numerical model
\cite{Murray2011} predicted a full-scale performance coefficient of 47\% at 1
m/s flow speed and a tip speed ratio $\lambda \equiv \frac{\omega R}{U_\infty} =
3.15$ \cite{Barone2011}, where $\omega$ and $R$ are the rotor's angular velocity
and radius, respectively. An initial experimental measurement campaign with a
1:15 scale RM2 rotor conducted at the Saint Anthony Falls Laboratory (SAFL) at
the University of Minnesota resulted in maximum power coefficient of
approximately 5\% at $\lambda = 2.2$. This discrepancy between numerical and
physical model performance prompted the experimental measurements presented
here, namely due to the low Reynolds number---$Re_D = U_\infty D / \nu$, where
$U_\infty$ is the free stream velocity, $D$ is the rotor diameter, and $\nu$ is
the fluid kinematic viscosity---of the 1:15 scale tests, which were performed at
$Re_D \sim 10^5$ \cite{Hill2014}.
